\subsection*{What is Leconte?}



Leconte is a computer system made to be utilized by the Oak Ridge National Laboratory for outreach. Currently, it consists of one N\+V\+I\+D\+IA Jetson T\+X2 circuit boards, but is planned to be expanded to a cluster of 8 Jetsons, the purpose of which is to demonstrate the powers and advantages of parallel computing. This serves as a simplified version of supercomputers at O\+R\+NL such as Summit or Frontier.

\subsection*{What is an N\+V\+I\+D\+IA Jetson?}

An N\+V\+I\+D\+IA Jetson T\+X2 is an embedded board made by N\+V\+I\+D\+IA that is built for robots and other maker projects. It is unique among other embedded boards in that it has 256 C\+U\+DA cores that make up its G\+PU. This allows it to run G\+P\+U-\/intensive tasks like machine learning or physics simulations much faster than a Raspberry Pi.

The Jetson runs a custom version of Ubuntu and has A\+R\+M-\/64 architecture.

This was the board of choice because it was the best evolution of the project, demonstrating the power of both distributed computing and G\+P\+Us.

\subsection*{Who made this?}

This app was developed by Tyler Duckworth and Logan O\textquotesingle{}Neal. Tyler worked primarily on the frontend of the application, designing and coding the G\+UI with Qt, an open-\/source C++ library. Logan worked on the three simulations that power this application\+: A smoke simulation, a fluid simulation, and a machine learning drawing demo.

This app was published under the G\+NU Public License v3 and is available on Git\+Hub. Scripts have been provided to properly configure the environment for this app. For any questions or comments on this project, email us, respectively, at \href{mailto:tyler.devtcn@gmail.com}{\texttt{ tyler.\+devtcn@gmail.\+com}} and \href{mailto:loganofneal@gmail.com}{\texttt{ loganofneal@gmail.\+com}}. 